---
title: "Targets_Workshop"
subtitle: "Establishing Pipilines with targets in R"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    css: custom.css 
    self_contained: false
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)

# save the built-in output hook
hook_output <- knitr::knit_hooks$get("output")

# set a new output hook to truncate text output
knitr::knit_hooks$set(output = function(x, options) {
  if (!is.null(n <- options$out.lines)) {
    x <- xfun::split_lines(x)
    if (length(x) > n) {
      # truncate the output
      x <- c(head(x, n), "....\n")
    }
    x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})

colorise <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}

```
***

# Introduction
Targets 

## What you will learn and why
Why you should use Targets:

* maintain a *reproducible workflow* 
* *save costly runtime* for tasks that are already up to date
* *provide evidence* that output aligns with the code and data

***

What you will learn in this workshop: 

* How to build a pipeline of custom functions using  `tar_script()` , `tar_edit()`and `tar_target()`
* How to visualize dependencies using `tar_visnetwork()` & `tar_manifest()`
* How to run your pipeline using  `tar_make()`
* How to  check for outdated targets using `tar_outdated()`
* How to access targets to work with them using `tar_read()`and  `tar_load()`
* How to monitor data files for changes by establishing them as targets



***
## A pipiline of functions , the Targets' Philosophy

A pipeline contains tasks to prepare datasets, run models, and summarize results for a business deliverable or research paper. The methods behind these tasks are user-defined R functions that live in R scripts, ideally in a folder called "R/" in the project. The tasks themselves are called “targets”, and they run the functions and return R objects. The targets package orchestrates the targets and stores the output objects to make your pipeline efficient, painless, and reproducible.
[Source](https://github.com/ropensci/targets)


```{r, fig.align='center', echo=F, out.width = "90%"}
#we could include a pipeline graphic here 
#  knitr::include_graphics("")
```


***
# Setup

Before we get started please lrun this chunk to load packages and delete any existing targets. 

```{r message=FALSE, comment=F}
pacman::p_load(kableExtra,
               tidyverse,
               targets,
               nycflights13,
               modelsummary
)
df<-nycflights13::flights

source("R/1-functions.R")
write.csv(df,"Data\\nyc_flights.csv", row.names = FALSE)
tar_destroy() # Start fresh, write 1 on the prompt in your console 
```

***
# Building a pipiline of custom functions




### Functions

The commands of your targets will depend on the functions from `1-functions.Rmd`. For the exercises below, they are in `R/1-functions.R`. 
Take a quick glance at `R/functions.R` familiarize yourself with the code base. 

### Start with a small pipeline.

The first version of the pipeline consists of three *targets*, or steps of computation. Our first targets do the following:

1. Reproducibly track the NYC flights data file.
2. Read in the data from the CSV file.
3. Build a simple linear model predicting delays.
4. Plot the model 
5. Report results


These steps are defined as custom functions in the `1-functions.Rmd`

### The `_targets.R` file
***

To initiating our targets, we express the computation in a special configuration file called `_targets.R` which has to be at the project's root directory. 
This file is necessary to: 

1. Load any functions and global objects that the targets depend on.
2. Set any options, including packages that the targets depend on.
3. Declare a list of targets using `tar_target()`. The `_targets.R` script must always end with a list of target objects.

You would create this file from scratch using the `tar_script()` command. 


```{r, fig.align='center', echo=F, out.width = "90%"}
#we could include a annotated picture of the tar_make file here

#  knitr::include_graphics("")
```


We have prepared and initial file for you here which you will edit throughout the workshop. 
Run the following code chunk to put our prepared  `_targets.R` file for this chapter in your working directory.


```{r, echo = TRUE, eval = FALSE}
file.copy("R/2-initial_targets.R", "_targets.R", overwrite = TRUE)

```


Now, open `_targets.R` in the RStudio  for editing. Exercises later in this chapter will ask you to make changes to this file. 

```{r}
library(targets)
tar_edit()
```



# Visualizing dependencies  |  `tar_visnetwork()` & `tar_manifest()` 

The `targets` package detects the relationships between targets automatically using static code analysis.

`tar_visnetwork()` includes functions in the dependency graph, as well as color-coded status information.
```{r}
tar_visnetwork()

```

While `tar_manifest()` provides a dataframe of your targets and its meta data e.g. name , R-command that runs it or its deployment priority.
```{r}
tar_manifest()
```



# Running the pipeline | `tar_make()`

So far we have been working on Set-up ...`tar_make()` actually runs the pipeline. 
It creates reproducible process that executes the targets in the `_targets.R` - file in the correct order (see the  dependency graph).

```{r}
get_data <- function(file) {
  read_csv(file, col_types = cols())
}
```


```{r}
tar_make()
```


# Accessing Targets | `tar_read()`and  `tar_load()`
There are other functions to access the targets and work with them in R or to report them. 


`tar_read()` reads a targets return value from, its file. For dynamik files it returns their path. 
```{r}
tar_read(run_lm)
```
`tar_read()` is useful to assign the target to a new object in case you want to work with it in R. 
```{r}
linear_model<-tar_read(run_lm)
mod_metrics(linear_model)
```


`tar_load()` loads the return values of a given target from its storage in _targets/objects.
```{r}
tar_load(run_lm)
```



# Checking for outdated targets | `tar_outdated()`

`tar_outdated()` checks the dependencies and data of targets and returns a list of outdated targets. 
If it returns 0 all our targets are up to date. 
```{r}
tar_outdated()
```

# Data files as targets 

In the targets scrip you can also specify a file as a target. In fact that is what we did with the *NYC-Flights* data set with `format = "file"` in `tar_target()`. This way any changes to the data set should trigger the target and all targets that depend on it to become outdated. 
`tar_read()` returns the path for these types of targets [targets with ].

```{r}
tar_read(flights_file)
```


#Questions 


1. What is the first thing you see when you open the 

2. Which is the first target that will run when you caall tar_make()?


3. After running this line of code what will happen? if you call tar_make()?  






# Add to the pipeline 


# Exercises

1. Add a plot target (we provide code )


2. Visualize the target.


3. Delete last row from the CSV file & check which targets are out dated .



4. Change the plot function (Change the dot color and type of dot in the plot.) 


5. Make a meaningless change to the Functions.RMD [delete a white space or and empty line]










# Sources & Further Resources

This tutorial drew heavily on the Materials provided by *Will Landau* the creator of Targets. 

*Helpful resources:*

* [Targets Manual](https://books.ropensci.org/targets/)
* [Targets Tutorial](https://github.com/wlandau/targets-tutorial)
* [Targets Video Series](https://www.youtube.com/watch?v=pbc6NX1n01Q&list=PLvgdJdJDL-APJqHy5CXs6m4N7hUVp5rb4)


*Styling and Structure* of the RMD have drawn on resources produced by Tom Arendt and Lisa Oswald produced for the Intro to Data Science Labs in 2021/22.

