---
title: "Custom functions for the customer churn workflow"
output: html_document
---

If you have not done so already, please view the slides at <https://wlandau.github.io/targets-tutorial> for an introduction to the `targets` R package.

# About



 These functions are the essential building blocks of the `targets` workflows to come.

1. `load_data()`: read the NYC-Flights data and split it into a training set and a test set.
2. `run_model()`: define a  model type and run on training data.
3. `get_fitted()`: get the models fitted values
3. `test_accuracy()`: get the accuracy of a fitted  model on the testing set.
4. `test_model()`: call `run_model()` and then `test_accuracy()`.


# NYC-Flights

Describe Dataset here 
# Packages

Our functions will need the following R packages. Run the code chunk below to load them.

```{r, message = FALSE}

library(tidyverse)

```


# `load_data()`



```{r}
load_data <- function(flights_file) {
  read_csv(churn_file, col_types = cols()) %>%
    initial_split(prop = 0.7) # from the rsample package
}
```

Try out the function.


