---
title: "Custom functions for the customer churn workflow"
output: html_document
---

If you have not done so already, please view the slides at <https://wlandau.github.io/targets-tutorial> for an introduction to the `targets` R package.

# About



 These functions are the essential building blocks of the `targets` workflows to come.

1. `load_data()`: read the NYC-Flights data and split it into a training set and a test set.
2. `run_model()`: specifis the values to run a linear model.
3. `get_plotted()`: get the models fitted values
3. `test_accuracy()`: get the accuracy of a fitted  model on the testing set.
4. `test_model()`: call `run_model()` and then `test_accuracy()`.


# NYC-Flights

Describe Dataset here 
# Packages

Our functions will need the following R packages. Run the code chunk below to load them.

```{r, message = FALSE}

library(tidyverse)
library(stargazer)

```


# `load_data()`

```{r}
load_data <- function(file) {
  read_csv(file, col_types = cols())
}
```

Try out the function.

```{r}
# Here we are specifying for the function to go to the folder Data and load the nyc_flights file.
data <- load_data("../Data/nyc_flights.csv")
str(data)
```

# `run_model`()`


```{r}
# Specifying a function that takes 1 dependant variable, and 2 independent ones 
run_lmodel <- function(y, x1, x2, data){
  lm(y ~ x1, data = data)
}
```

```{r}
a <- run_lmodel(data$arr_delay, data$dep_delay, data = data)
```



```{r}
plot(data$dep_delay, data$arr_delay, pch = 1, col = 'steelblue') + abline(a)
```
```{r}
stargazer(a, type = "text")
```

