---
title: "Targets_Workshop"
subtitle: "Establishing Pipilines with targets in R"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    css: custom.css 
    self_contained: false
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)

# save the built-in output hook
hook_output <- knitr::knit_hooks$get("output")

# set a new output hook to truncate text output
knitr::knit_hooks$set(output = function(x, options) {
  if (!is.null(n <- options$out.lines)) {
    x <- xfun::split_lines(x)
    if (length(x) > n) {
      # truncate the output
      x <- c(head(x, n), "....\n")
    }
    x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})

colorise <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}

```
***

# Introduction
Targets 

## What you will learn and why
Why you should use Targets:

* maintain a *reproducible workflow* 
* *save costly runtime* for tasks that are already up to date
* *provide evidence* that output aligns with the code and data

What you will learn in this workshop: 
* How to build a pipeline of custom functions using  `tar_script()` , `tar_edit()`and `tar_target()`
* How to visualize dependencies using `tar_visnetwork()` & `tar_manifest()`
* How to run your pipeline using  `tar_make()`
* How to  check for outdated targets using `tar_outdated()`
* How to access targets to work with them using `tar_read()`and  `tar_load()`
* How to monitor data files for changes by establishing them as targets


??* How to debug in targets ??


***
## A pipiline of functions , the targets Philosophy

A pipeline contains tasks to prepare datasets, run models, and summarize results for a business deliverable or research paper. The methods behind these tasks are user-defined R functions that live in R scripts, ideally in a folder called "R/" in the project. The tasks themselves are called “targets”, and they run the functions and return R objects. The targets package orchestrates the targets and stores the output objects to make your pipeline efficient, painless, and reproducible.
[Source](https://github.com/ropensci/targets)


```{r, fig.align='center', echo=F, out.width = "90%"}
#we could include a pipeline graphic here 
#  knitr::include_graphics("")
```


***
# Setup

Before we get started please lrun this chunk to load packages and delete any existing targets. 

```{r, message=F, comment=F}
pacman::p_load(kableExtra,
               tidyverse,
               targets,
               nycflights13
)
df<-nycflights13::flights

write.csv(df,"..\\Data\\nyc_flights.csv", row.names = FALSE)

tar_destroy() # Start fresh.
```

***
# Building a pipiline of custom functions




## Functions

The commands of your targets will depend on the functions from `1-functions.Rmd`. For the exercises below, they are in `R/1-functions.R`. 
Take a quick glance at `R/functions.R` familiarize yourself with the code base. 

## Start with a small pipeline.

The first version of the pipeline consists of three *targets*, or steps of computation. Our first targets do the following:

1. Reproducibly track the NYC flights data file.
2. Read in the data from the CSV file.
3. Build a simple linear model predicting delays.
4. Plot the model 
5. Report results


These steps are defined as custom functions in the `1-functions.Rmd`

## The `_targets.R` file
***

To initiating our targets, we express the computation in a special configuration file called `_targets.R` which has to be at the project's root directory. 
This file is necessary to: 

1. Load any functions and global objects that the targets depend on.
2. Set any options, including packages that the targets depend on.
3. Declare a list of targets using `tar_target()`. The `_targets.R` script must always end with a list of target objects.

You would create this file from scratch using the `tar_script()` command. 


```{r, fig.align='center', echo=F, out.width = "90%"}
#we could include a annotated picture of the tar_make file here

#  knitr::include_graphics("")
```


We have prepared and initial file for you here which you will edit throughout the workshop. 
Run the following code chunk to put our prepared  `_targets.R` file for this chapter in your working directory.


```{r, echo = FALSE}
file.copy("initial_targets.R", "_targets.R", overwrite = TRUE)
```

Now, open `_targets.R` in the RStudio  for editing. Exercises later in this chapter will ask you to make changes to this file. 

```{r}
library(targets)
tar_edit()
```



# Visualizing dependencies 



# Running the pipeline



# Accessing Targets 


# Checking for outdated targets




#Questions 


1. What is the first thing you see when you open the 

2. Which is the first target that will run when you caall tar_make()?


3. After running this line of code what will happen? if you call tar_make()?  






# Add to the pipeline 


# Exercises

1. Add a generalized linear model and analyse its performance. 
  a) add a run_glm target to the  `_targets.R` file 
  b) add the results to the Report.RMD


2. Visualize the target.



3. Delete last row from the CSV file & check which targets are out dated .













# Sources & Further Resources

This tutorial drew heavily on the Materials provided by *Will Landau* the creator of Targets. 
*Helpful resources:* 
* [Targets Manual](https://books.ropensci.org/targets/)
* [Targets Tutorial](https://github.com/wlandau/targets-tutorial)
* [Targets Video Series](https://www.youtube.com/watch?v=pbc6NX1n01Q&list=PLvgdJdJDL-APJqHy5CXs6m4N7hUVp5rb4)




