---
title: "Custom functions the NYC-flights linear modeling workflow"
output: html_document
---


# About



 These functions are the essential building blocks of the `targets` workflows to come.

1. `load_data()`: read the NYC-Flights data and split it into a training set and a test set.
2. `run_model()`: specifis the values to run a linear model.
3. `plot_mod()`: get the models fitted values
4. `mod_metrics()`: get the key metrics of your linear model.


# NYC-Flights

Describe Dataset here 
# Packages

Our functions will need the following R packages. Run the code chunk below to load them.

```{r, message = FALSE}

library(tidyverse)
library(modelsummary)

```


# `load_data()`

```{r}
load_data <- function(file) {
  read_csv(file, col_types = cols())
}
```

Try out the function.

```{r}
# Here we are specifying for the function to go to the folder Data and load the nyc_flights file.
data <- load_data("../2-data/nyc_flights.csv")
```

# `run_model()`

```{r}
# Specifying a function that takes 1 dependant variable, and up to 3 independent ones 
run_lmodel <- function(y, x1, x2, x3, data = data, n_var = 1){
  if (n_var == 1){ # 1 independent variable
    lm(y ~ x1, data = data)
  }else if ( n_var == 2){ # 2 independent variables
    lm(y ~ x1 + x2, data = data)
  } else if(n_var == 3){ # 3 independent variables
    lm(y ~ x1 + x2 + x3, data = data)
  } else{ # error message
    print("n_var not specified or out of range, valid values [1-3]")
  }
}
```

```{r}
a <- run_lmodel(data$arr_delay, data$dep_delay, data$carrier, data$distance, data = data, n_var = 3)
b <- run_lmodel(data$arr_delay, data$dep_delay, data = data)
```


# `plot_mod()`

```{r}
plot_mod <- function(x_axis, y_axis,lm = lm, c = 'red1', x_lab = "x-axis", y_lab = "y-axis"){
  plot(x_axis, y_axis, pch = 1, col = c, xlab = x_lab, ylab = y_lab) + 
    abline(lm)
  }
```


```{r}
plot_mod(data$dep_delay, data$arr_delay, lm = b, x_lab = "Departing Delay", y_lab = "Arriving Delay")
```
# `mod_metrics()`

```{r}
mod_metrics <- function(lm = lm){
  stargazer(lm, type = "text")
}
plot(data$dep_delay, 
     data$arr_delay, 
     xlab="X axis title",
     ylab="Y axis title")
```

```{r}
mod_metrics(a)
```



